Air raids on the UK: understanding the effect of time on casualties

### 2024-12-04 paper/paper.qmd
updated

This study uses the [@airraids] dataset to study the relationship between variables such as time to casualties.

I used the statistical programming language R [@citeR] for data cleaning and analysis. The R packages used were **usethis** for file paths [@usethis], **`tidyverse`** for data manipulation and visualization [@tidyverse], **`here`** for file path management [@here], **`lubridate`** for date handling [@lubridate], **`arrow`** for data storage and processing [@arrow], **`testthat`** for unit testing [@testthat], **`readr`** for reading structured data [@readr], **`dplyr`** for data manipulation [@dplyr], **`stringr`** for string operations [@stringr], **`ggplot2`** for creating visualizations [@ggplot2], **`brms`** for modeling [@brms], and **`modelsummary`** for summarizing models and results [@modelsummary].

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(modelsummary)

# Summarize the first model
first_model <-
  readRDS(file = here::here("models/first_model.rds"))

modelsummary(first_model, 
             statistic = c("estimate", "std.error", "conf.low", "conf.high"))

```

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

Please don't use these as sub-heading labels - change them to be what your point actually is.

>>>>

This study uses the [@britainbombing] dataset to study the relationship between variables such as time to casualties.

I used the statistical programming language R [@citeR] for data cleaning and analysis. The R packages used were **usethis** for file paths [@usethis], **`tidyverse`** for data manipulation and visualization [@tidyverse], **`here`** for file path management [@here], , **`arrow`** for data storage and processing [@arrow], **`testthat`** for unit testing [@testthat], **`readr`** for reading structured data [@readr], **`dplyr`** for data manipulation [@dplyr], , **`ggplot2`** for creating visualizations [@ggplot2], **`brms`** for modeling [@brms], and **`modelsummary`** for summarizing models and results [@modelsummary].

@@

@@

@@
